\documentclass[]{article}

% Packages for mathematics
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{bm}
\usepackage{authblk}

% Package for graphics
\usepackage{graphicx}
\graphicspath{{../figures/}}
\usepackage{subcaption}
\usepackage{placeins}


% Package for page layout and headers/footers
%\usepackage{geometry}
%\geometry{margin=1in}

\usepackage{mathrsfs}
% Package for clickable links
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue,
}

% Package for algorithms
\usepackage{float}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{matlab-prettifier}
\usepackage{tabularx}
\usepackage{amsmath, physics}

% Custom theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}

\title{Functional Analysis (MA 8673) Homework 4}
\author{Kevin Ho}
\date{\today}

\begin{document}

\maketitle

\begin{enumerate}
    \item Consider the one-parameter unitary group given by $U(t)f(x) = f(x-t \text{ mod } 2\pi)$ for $f\in L^2(0,2\pi).$ What is the generator of $U$?


    \item Suppose $M$ is the Riemann surface of $\sqrt{z}$ and $\mathcal{H}  \in L^2(M)$ with Lebesgue measure locally. Define the following two operators:

    $$
    A = -i\frac{\partial}{\partial x} \text{ and } -i\frac{\partial}{\partial x} 
    $$

    both with domain $\mathcal{D} = \{ f \in C^\infty(M): \text{supp}(f) \text{ is compact}, 0\notin \text{supp}(f)\}$. Prove that both $A$ and $B$ are essentially self-adjoint, both $A,B:\mathcal D \rightarrow \mathcal D$, and $(AB)f = (BA)f, \text{ } \forall f\in \mathcal D$. However show that exp($it\overline{A}$) and exp($it\overline{B}$) do not commute.

    \item Let $\mu$ be a finite complex Borel measure on $\mathbb{R}$ and let 

    $$
    \hat{\mu}(t) = \int_\mathbb{R} e^{-it\lambda} d\mu(\lambda).
    $$
    Prove that 
    $$
    \lim_{c\rightarrow\infty} \frac{1}{c} \int_0^c|\hat{\mu}(t)|^2dt = \sum_{\lambda \in \mathbb{R}} |\mu (\{\lambda\})|^2
    $$

    where the sum on the right hand side is finite.




    \begin{proof}
        So let's start by decomposing the LHS.
    \end{proof}

    \item Let $A$ be a self-adjoint operator. Using the previous problem, prove that $\lim_{t\rightarrow \infty}U(t)= 0$ where $U(t) = exp($-it{A}$)$
    
    \item Let $X$ be a infinite dimensional locally convex space and $X^*$ its dual space. Prove that no weakly continuous semi-norm is actually a norm. (This shows semi-norms are essential tools.)

    \item Let $\{\rho_\alpha\}_{\alpha \in A}$ be a family of semi-norms so that some finite sum $\rho_{\alpha_1} + \dots + \rho_{\alpha_n}$ is actually a norm. Prove that $\{\rho_\alpha\}_{\alpha \in A}$ is equivalent to a family of norms. 





\end{enumerate}

\end{document}
